\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-24 phd-cs-us.tex
Updates from Overleaf

This is one of the most common questions that international students often have. Faculty often received many mails from international students about admission, TA, RA and various related topics. Most of the time, we ignore these emails; but sometimes, we do answer them.  So under what cases we would answer and would not?

@@

If you want to contact a prof. to ask about \emph{research opportunities}, then \emph{may be}.  First, you should read the prof's website, see if they are saying something about contacting them. Many profs. indicate what you should do to contact them (e.g., specific email subjects). In general cases, you need to \emph{customize your email}. For example, read their papers, and see if you are interested in their work.  If you are, then you can send them an email talking how/why their work would match yours (give details and evidence, don't just say I am a software developer and therefore match with your interests in software design) and ask about research opportunities.

>>>>

This is a common question that international students have. Faculty often received many mails from international students about admission, TA, RA and various related topics. Most of the time, we ignore these emails; but sometimes, we do answer them.  So when we usually respond and when we do not?

@@

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{GTA/GRA} support, then \emph{may be}.  The best way to catch the prof.'s attention you is to \emph{customize your email} to that specific faculty.  For example, read their papers, and see if you are interested in their work.  If you are, then you can send them an email talking how/why their work would match yours (give details and evidence, don't just say I am a software developer and therefore match with your interests in software design) and ask about research opportunities. Also, don't feel bad if they do not reply.

You should also read the prof's website, see if they are saying something about contacting them. Many profs. indicate what you should do to contact them (e.g., specific email subjects).
